---
title: "Codebook"
author: "Ashok"
date: "November 20, 2015"
output: html_document
---

# CodeBook

The file tidydataset.txt contains the tidy data set prepared for Coursera Assigment. 

  This is a modified subset of the original data set which can be obtained from 
https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip 
  A full description of original dataset can be obtained at 
http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones 


  This tidy data set contains rows, each having values only for the mean and standard deviation of the feature set described in feature_info.txt of original dataset.
  
  Naming convention of Columns is available in feature_info.txt of original dataset. This tidy dataset also adheres to same naming convention.
'-XYZ' is used to denote 3-axial signals in the X, Y and Z directions.

  Available list of columns
```{r echo=FALSE}
dt <- read.table("tidydataset.txt", header = TRUE, check.names = FALSE)
names(dt)
```

Dimensions
```{r}
dim(dt)
```


  Summary of table
```{r}
str(dt)
```


###References
[1] Davide Anguita, Alessandro Ghio, Luca Oneto, Xavier Parra and Jorge L. Reyes-Ortiz. Human Activity Recognition on Smartphones using a Multiclass Hardware-Friendly Support Vector Machine. International Workshop of Ambient Assisted Living (IWAAL 2012). Vitoria-Gasteiz, Spain. Dec 2012