---
title: "Codebook"
author: "Ashok"
date: "November 20, 2015"
output: html_document
---

# CodeBook

The file tidydataset.txt contains the tidy data set prepared for Coursera Assigment.  
  
This is a modified subset of the original data set which can be obtained from 
https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip  
A full description of original dataset can be obtained at 
http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones 


## Dataset Description  

* Column 1: Suject_id is to identify the subject whose movements were measured
* COlumn 2: Activity is the Name of the activity that was performed at the time of measurement
* Columns 3:68 are Average and Standard Deviations of the feature sets desribed in original dataset.
  
  
Naming convention of features is available in feature_info.txt of original dataset.  
  
### Summary of Naming Convention  
* -XYZ is used to denote 3-axial signals in the X, Y and Z directions.
* prefix 't' denotes time domain
* prefix 'f' denotes frequency domain (obtained by applying a Fourier Transformation to some of the Signals )


## Feature list
  
* tBodyAcc-XYZ
* tGravityAcc-XYZ
* tBodyAccJerk-XYZ
* tBodyGyro-XYZ
* tBodyGyroJerk-XYZ
* tBodyAccMag
* tGravityAccMag
* tBodyAccJerkMag
* tBodyGyroMag
* tBodyGyroJerkMag
* fBodyAcc-XYZ
* fBodyAccJerk-XYZ
* fBodyGyro-XYZ
* fBodyAccMag
* fBodyAccJerkMag
* fBodyGyroMag
* fBodyGyroJerkMag

### The set of variables that were estimated from these signals are: 

* mean(): Mean value
* std(): Standard deviation

## Available list of Columns
```{r echo=FALSE}
dt <- read.table("tidydataset.txt", header = TRUE, check.names = FALSE)
names(dt)
```


Dimensions
```{r}
dim(dt)
```


  Summary of table
```{r}
str(dt)
```


###References
[1] Davide Anguita, Alessandro Ghio, Luca Oneto, Xavier Parra and Jorge L. Reyes-Ortiz. Human Activity Recognition on Smartphones using a Multiclass Hardware-Friendly Support Vector Machine. International Workshop of Ambient Assisted Living (IWAAL 2012). Vitoria-Gasteiz, Spain. Dec 2012